### 2021-02-17 evaluation.tex
Remove a commented-out redundant paragraph
Move a todo
Reference "saturation iterations" from Evaluation

%For the experiment, Vampire 4.3.0 was modified to convert the problems from the \gls{tptp} format to a representation that allows easy automated processing.
%More precisely, when the modified prover is run in the clausification mode (\texttt{vampire -mode clausify}),
%it outputs the \gls{cnf} form of the problem and the problem signature in formats that allow easy processing in Python.
%The \gls{cnf} clause and term structure of the problem is encoded into the \gls{json} format,
%and the signature along with additional symbol metadata is encoded into the \gls{csv} format.

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
\todo{FB: Reference a detailed explanation of saturation loop iterations. MS: podobne jako v PAAR clanku. Dal bych to nekam okolo prelim.}

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$$
\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}
$$
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail? MS: Myslim, ze takhle v kontextu uz dobry. Pusobi to hezky dojmem, 
ze kdyz to nechapes, je to jen tim, zes necetl prislusne clanky. A zaroven jde tusit, ze to jsou pomerne
standardni veci, ktere sice ovlivni dataset, ale zakldni myslenku ``ucit se z nahodnych permutaci'' nijak zasadne nemeni.}

>>>>

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}

@@

To ensure the efficiency of the sampling, the process is interpreted as an instance of Bernoulli multi-armed bandit problem,
\todo{Cite? MS: kdyz bude dobra citace, sem by se urcite sikla:) Pri nejhorsim Sutton \& Barto to jisti.}
with the reward of a trial being 1 in case an example is produced, and 0 otherwise.
Adaptive sampling balances
exploring problems that have been tried relatively scarcely and
exploiting problems that have yielded examples relatively often.
For each problem $P \in \ProblemsTptp$,
the generator keeps track of the number of times the problem has been tried $n_P$
and the number of examples generated from that problem $s_P$.
The ratio of $s_P$ to $n_P$ corresponds to the average reward of problem $P$ observed so far.
The problems are sampled using the allocation strategy \acrshort{ucb1} \cite{Auer2002} with a parallelizing relaxation.
In each iteration, the generator samples the problem $P$ that maximizes
$$
\frac{s_P}{n_P} + \sqrt{\frac{2 \ln n}{n_P}}
$$
where $n = \sum_{P \in \ProblemsTptp} n_P$ is the total number of tries on all problems.
The parallelizing relaxation means that the $s_P$ values are only updated once in \num{1000} iterations,
allowing up to \num{2000} parallel solver executions.
\todo{Explain in detail?}
